\documentclass[a4paper,10pt]{article}

% Make ATS friendly
\pdfgentounicode=1

% Remove section numbering
\setcounter{secnumdepth}{0}

% Packages
\usepackage{geometry}
\usepackage[bookmarks=false]{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{enumitem}

% Colour code
\definecolor{Fuchsia}{HTML}{582C83}

% Geometry
\geometry{
    a4paper,
    top=0.4cm,
    bottom=0.4cm,
    left=0.4cm,
    right=0.4cm
}

% Hyperlink setup
\hypersetup{ 
    colorlinks=true,
    urlcolor=blue,
    pdftitle={My Resume},
}

% Document
\begin{document}

% Full name
\begin{center}
    {\Huge\scshape {\color{Fuchsia}\textbf {SHREE HARI ANBAZHAGAN}}}
\end{center}
\vspace{-6mm}
% Address
\begin{center}
    \small{Chennai, Tamil Nadu - 600106, India}
\end{center}
\vspace{-6mm}
% Contact details
\begin{center}
    \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l c r @{}}
        \small{\faLinkedin \ \href{https://www.linkedin.com/in/a-shreehari/}{linkedin.com/in/a-shreehari}} &
        \small{\faIcon{mobile-alt} \ \href{tel:+917667899999}{+91 7667899999}} &
        \small{\faEnvelope \ \href{mailto:shreeharianbazhagan@gmail.com}{shreeharianbazhagan@gmail.com}} 
    \end{tabular*}
\end{center}

\hrule
\vspace{-4mm}
% Experience details
\section{\scshape\color{Fuchsia}{\faUserTie\ \textbf EXPERIENCE}}
% FTE Comcast
\textbf{Comcast} \href{https://corporate.comcast.com/}{\faIcon{link}} \hfill
\textit{July 2023 - present} \\
\textbf{Development Engineer 1}, Data Engineer \hfill \textit{Chennai, India}
\vspace{-2mm}
\begin{itemize}
    \item Led the development and maintenance of ETLs for internal and external teams, integrating Kafka with AWS Redshift, ensuring near-zero downtime and improved system reliability.
    \vspace{-2mm}
    \item Architected and deployed multiple solutions using \textbf{infrastructure as code (IaC)} and \textbf{draw.io}, following best practices for \textbf{scalability, security, and automation}, resulting in a \textbf{30\% reduction in deployment time and effort}.
    \vspace{-2mm}
    \item Designed and deployed data synchronization tools (\textbf{EnvSyncer}) to ensure consistency across \textbf{Data Warehouses}, implementing anomaly detection with AWS Lookout Metrics, and building \textbf{reconciliation frameworks} that improved data accuracy by \textbf{40\%}.
\end{itemize}
\vspace{-2mm}
% Intern Comcast
\textbf{Comcast} \href{https://drive.google.com/file/d/1pad_OUtVNHKm3s1Kb-_xwyZAXJBjz7gX/view?usp=sharing}{\faIcon{link}} \hfill \textit{Jan 2023 - June 2023} \\
\textbf{Intern} \hfill \textit{Chennai, India}
\vspace{-2mm}
\begin{itemize}
    \item Developed a \textbf{Slack notification system} to monitor ETL runs and job status, providing real-time alerts and daily cost breakdowns to enhance operational efficiency.
    \vspace{-2mm}
    \item Assisted and leant of a Data Warehouse (DWH) application to create a single source of truth for organizational data.
\end{itemize}
\vspace{-2mm}
% Intern L&M
\textbf{Lasso and Marquee Design Solutions} \href{https://drive.google.com/file/d/1fMTBkQUhU6_34D5mxVZRf7wBHGMJPdVi/view?usp=sharing}{\faIcon{link}} \hfill \textit{June 2019 - July 2019} \\
\textbf{Intern} \hfill \textit{Chennai, India}
\vspace{-2mm}
\begin{itemize}
    \item The internship provided valuable insights into IT operations, teamwork, and professional communication.
\end{itemize}

\hrule
\vspace{-4mm}
% Education details
\section{\scshape\color{Fuchsia}{\faGraduationCap\ \textbf EDUCATION}}
% IITM
\textbf{Indian Institute of Technology Madras} \href{https://drive.google.com/file/d/1HUZf7LIsTZaPjUkf3tKMAnduHmgObdS1/view?usp=sharing}{\faIcon{link}} \hfill \textit{Sep 2023 - present} \\
\textbf{Diploma in Data Science} \hfill \textit{Chennai, India} \\
Gaining expertise in analytics, machine learning, and big data technologies through the program. \\
% sastra
\textbf{SASTRA Deemed University} \href{https://drive.google.com/file/d/1phkkQpvXzo3_0dZZnujCL_nOU1YJfxKO/view?usp=sharing}{\faIcon{link}} \hfill \textit{July 2019 - May 2023} \\
\textbf{Bachelor of Technology in Computer Science \& Engineering,} \hfill \textit{Thanjavur, India} \\
Graduated First Class with Distinction. \\

\hrule
\vspace{-4mm}
% Project details
\section{\scshape\color{Fuchsia}{\faLaptopCode\ \textbf PROJECTS}}
% IITM MLP project
\textbf{IITM Machine learning project} \href{https://github.com/ShreehariA/IITM_MLP_Project}{\faIcon{link}} \hfill \textit{Sep 2024 - Nov 2024}
\vspace{-2mm}
\begin{itemize}
    \item Built models to predict bank telemarketing success.
    \vspace{-2mm}
    \item Performed \textbf{EDA and preprocessing} based on insights, \textbf{trained 4 models}, and achieved the best results with an \textbf{accuracy of 87\%} and a macro F1 score of 0.75, with notable performance in precision and recall for the 'no' class.
\end{itemize}
\vspace{-2mm}
% G20 library summit
\textbf{Sentiment Analysis and Topic Modeling for Tweets} \href{https://github.com/ShreehariA/G20_Library_Summit}{\faIcon{link}} \hfill \textit{Dec 2023 - Feb 2024}
\vspace{-2mm}
\begin{itemize}
    \item Contributed to the ML project "Inside Out – Understanding User Emotions," focusing on sentiment and topic analysis of tweets, with findings presented at the \textbf{G20 Library Summit 2024}.
    \vspace{-2mm}
    \item Developed an Excel sheet with base data and analysis results, covering sentiment analysis, topic modeling, and engagement metrics. incorporating visualizations like heat maps and graphs to highlight data trends.
    \vspace{-2mm}
    \item Used \textbf{pysentimiento} for sentiment analysis and \textbf{cardiffnlp/tweet-topic-21-multi} for topic modeling, achieving \textbf{94.53\% accuracy} in extracting insights from tweets.
\end{itemize}
\vspace{-2mm}
% SASTRA project
\textbf{Diabetes prediction} \href{https://github.com/ShreehariA/diabetes-pred}{\faIcon{link}} \hfill \textit{Sep 2022 - Dec 2023}
\vspace{-2mm}
\begin{itemize}
    \item Developed a \textbf{Django web application} for \textbf{diabetes prediction}, leveraging multiple \textbf{machine learning algorithms} (\textbf{Logistic Regression, Random Forest, Adaboost}, etc.) to provide accurate predictions based on user health metrics.
    \vspace{-2mm}
    \item Integrated \textbf{PDF report generation} and \textbf{SMS notification features} within the application, with the model achieving an \textbf{accuracy score of 0.82 for Random Forest} and \textbf{0.80 for Adaboost}, enhancing user experience by delivering prediction results in both \textbf{downloadable} and \textbf{mobile-friendly formats}.
\end{itemize}
\vspace{-2mm}
% % Personal project
% \textbf{Helpers} \href{https://github.com/ShreehariA/helpers}{\faIcon{link}} \hfill \textit{Sep 2023 - present}
% \vspace{-2mm}
% \begin{itemize}
%     \item Created a personal project involving \textbf{reusable helper classes} for \textbf{AWS, API integration, Kafka, and Slack}, improving system automation and data operations.
%     \vspace{-2mm}
%     \item Developed efficient \textbf{data pipelines} with \textbf{S3, Athena, Redshift, and Kafka integrations} in a personal project, optimizing \textbf{data retrieval, transformation}, and \textbf{real-time streaming} for enterprise applications.
% \end{itemize}
% Others
\textbf{Other projects}
\vspace{-2mm}
\begin{itemize}
    \item \textbf{Helper} \href{https://github.com/ShreehariA/helpers}{\faIcon{link}} Created a personal project involving \textbf{reusable helper classes} for \textbf{AWS, API integration, Kafka, and Slack}.
    \vspace{-6mm}
    \item \textbf{IITM Business Data Management project} \href{https://github.com/ShreehariA/IITM_BDM_Project}{\faIcon{link}} Aims to tackle business challenges by leveraging data management and analysis techniques.
    \vspace{-2mm}
    \item \textbf{Resume} \href{https://github.com/ShreehariA/Resume}{\faIcon{link}} My LaTeX resume.
\end{itemize}

\hrule
\vspace{-4mm}
% Techinical skills details
\section{\scshape\color{Fuchsia}{\faTools\ \textbf TECHNICAL SKILLS}}
\textbf{Programming}: Python, SQL, Terraform (Infrastructure as Code), shell commands (basic), YAML, JSON. \\
\textbf{Tools and Frameworks}: AWS (AWS Lambda, Glue, S3, Redshift, Athena, IAM (Roles, Policies), Secrets Manager, CloudWatch), Boto3 (AWS API), REST API, PostgreSQL
, Docker, Kafka, Machine Learning (ML), Git, VSCode, JIRA, Excel.
\end{document}
